Carbonate chemistry at Ny-Ålesund

### 2022-01-17 awipev-CO2.Rmd
Sorting sections K1K2 out. In progress

# calculate typical uncertainty assuming uncertainties of 3 uatm for pCO2 and 4 umol/kg for AT and CT
errors_pco2_at <- seacarb::errors(flag=24, var1=mean_pco2, var2=1e-6*mean_at, S=mean_sal,
                          T=mean_temp, P=0, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T",
                          b="u74", evar1=3, evar2 = 4e-6)
errors_at_ct <- seacarb::errors(flag=15, var1=1e-6*mean_at, var2=1e-6*mean_ct, S=mean_sal,
                          T=mean_temp, P=0, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T",
                          b="u74", evar1=4e-6, evar2 = 4e-6)
errors <- tibble(e_pH = c(errors_pco2_at$pH, errors_at_ct$pH),
                 e_pCO2 = c(NA, errors_at_ct$pCO2),
                 e_DIC = c(errors_pco2_at$pH, NA)*1e3,
                 e_Oa = c(errors_pco2_at$OmegaAragonite, errors_at_ct$OmegaAragonite)
)
# impacts using pco2 and AT pair
carb_l_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_1 <- carb_l_1 - carb_s_1
# impacts using AT-CT pair
carb_l_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = 0, 
                k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_2 <- carb_l_2 - carb_s_2
# summary
const_choice <- bind_rows(diff_ls_1, diff_ls_2) %>% 
  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
                S = mean_sal,
                T = mean_temp,
                DIC = DIC * 1e6
                ) %>% 
  dplyr::select(flag, pH, pCO2, DIC, OmegaAragonite) %>% 
  dplyr::bind_cols(errors)
```

### K1K2 using pCO2 and AT

@@

#### Difference Lueker vs Sulpis

@@

#### Difference between all formulations and measured pH

@@

### K1K2 using CT and AT

@@

#### Difference Lueker vs Sulpis

>>>>

# calculate typical uncertainty assuming uncertainties of 3 uatm for pCO2 and 4 umol/kg for AT and CT
errors_pco2_at <- seacarb::errors(flag=24, var1=mean_pco2, var2=1e-6*mean_at, S=mean_sal,
                          T=mean_temp, P=0, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T",
                          b="u74", evar1=3, evar2 = 4e-6)
errors_at_ct <- seacarb::errors(flag=15, var1=1e-6*mean_at, var2=1e-6*mean_ct, S=mean_sal,
                          T=mean_temp, P=0, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T",
                          b="u74", evar1=4e-6, evar2 = 4e-6)
errors <- tibble(e_pH = c(errors_pco2_at$pH, errors_at_ct$pH),
                 e_pCO2 = c(NA, errors_at_ct$pCO2),
                 e_DIC = c(errors_pco2_at$pH, NA)*1e3,
                 e_Oa = c(errors_pco2_at$OmegaAragonite, errors_at_ct$OmegaAragonite)
)
# impacts using pco2 and AT pair
carb_l_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_1 <- carb_l_1 - carb_s_1
# impacts using AT-CT pair
carb_l_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = 0, 
                k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_2 <- carb_l_2 - carb_s_2
# summary
const_choice <- bind_rows(diff_ls_1, diff_ls_2) %>% 
  dplyr::mutate(flag = c("pCO2-AT", "AT-CT"),
                S = mean_sal,
                T = mean_temp,
                DIC = DIC * 1e6
                ) %>% 
  dplyr::select(flag, pH, pCO2, DIC, OmegaAragonite) %>% 
  dplyr::bind_cols(errors)
```

### All K1K2 using pCO2-AT

@@

@@

@@

### All K1K2 using CT and AT

@@

### Lueker vs Sulpis discrete
